\documentclass{article}
\input{mydefs}

\usepackage{fullpage}

\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}


\title{Python Exercises for Ghayoung and Beth}
\author{Sunghee}


\begin{document}
\maketitle

\section{Basic exercises}

\begin{description}
\item[Exercise 01]
\href{https://www.practicepython.org/exercise/2014/01/29/01-character-input.html}{Character Input}

\item[Exercise 02]
\href{https://www.practicepython.org/exercise/2014/02/05/02-odd-or-even.html}{Odd or Even}

\item[Exercise 03]
\href{https://www.practicepython.org/exercise/2014/02/26/04-divisors.html}{Divisors}

\item[Exercise 04]
Create a program that asks the user for a number and then prints out all prime numbers that is less than that number.
(Hint: Think of the definition of a prime number. You can use the piece of code you developed for one of the above problems.
You will need to use nested for-loops. Ask your instructor if you don't know what nested for-loops are.)

\item[Exercise 04.1]
Implement a function which takes two numbers, adds them, and returns the result.

\item[Exercise 04.2]
Implement a function which takes one integer and returns {\tt True} if it is an even number,
and return {\tt False} otherwise.

\item[Exercise 04.3]
Implement a function which takes one integer and prints all its divisors.

\item[Exercise 04.4]
Implement a function named \verb+is_prime+ which takes one integer and returns {\tt True} if it is a prime number,
and return {\tt False} otherwise.

\item[Exercise 04.5]
Create a program that asks the user for a number and then prints out all prime numbers that is less than that number
using a function you implemented above.

\item[Exercise 05 (Optional)]
Make the prime number printing program more efficient following the steps below.

\begin{enumerate}
\item Make \verb+is_prime+ faster by cutting down the size of the \verb+for+-loop into half,
\ie, by changing the \verb+for+-loop as follows:
\begin{verbatim}
    for divisor in range(2, int(number/2) + 1):
        ...
\end{verbatim}

\item Make \verb+is_prime+ faster by cutting down the size of the \verb+for+-loop even further
as follows.
\begin{verbatim}
    import math

    for divisor in range(2, int(math.sqrt(number)) + 1):
        ...
\end{verbatim}

Can you explain why this works?

\item (Advanced) Make \verb+is_prime+ faster by only checking whether the number is divided by primer numbers less than or equal to
the square root of the number.

\end{enumerate}
\end{description}


\section{Intermediate-level exercises}

\begin{enumerate}
\item 
\href{https://www.practicepython.org/exercise/2014/03/05/05-list-overlap.html}{List Overlap}

\item
\href{https://www.practicepython.org/exercise/2014/03/12/06-string-lists.html}{String Lists}

\end{enumerate}


\end{document}
